Out-of-Sample Comparisons of Overfit Models

### 2012-03-30 mc/plot-insample-size.Rnw
Typed up changes to paper

\documentclass{article}
\SweaveOpts{prefix.string=plots/ftest}
\usepackage[margin=1in]{geometry}

@@

<<fig=TRUE,width=5.5, height=4>>=
library(fwPackage)
library(lattice)
ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
ltheme$strip.background$col <- "transparent" ## change strip bg  
lattice.options(default.theme = ltheme)      ## set as default

@@

print(dotplot(norm ~ reject | interaction(altlabel,nlabel, sep = ", "),
              dat = d, las = 1,
              xlab = "Rejection Probability", ylab = "c",
              xlim = c(-.1, 1.1),
              panel = function(x, y, ...) {
                panel.dotplot(x, y, ..., type = "n")
                panel.text(x, as.numeric(y), labels = sprintf("%.2f", x))
              },
              par.strip.text = list(cex = .65),
              layout = c(2,4),
              index.cond = list(c(3,4,7,8,5,6,1,2))))
@

>>>>

\documentclass{article}
\SweaveOpts{prefix.string=plots/ftest}
\usepackage[margin=1in]{geometry}
\usepackage{tikz}

@@

<<fig=TRUE,width=5.5, height=4, eps=F, pdf=T>>=
library(fwPackage)
library(pgfSweave)
library(lattice)
ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
ltheme$strip.background$col <- "transparent" ## change strip bg  
lattice.options(default.theme = ltheme)      ## set as default

@@

print(dotplot(norm ~ reject | interaction(altlabel,nlabel, sep = ", "),
              dat = d, las = 1,
              xlab = "Rejection Probability", ylab = "c",
              xlim = c(-.1, 1.1),
              panel = function(x, y, ...) {
                panel.dotplot(x, y, ..., type = "n")
                panel.text(x, as.numeric(y), labels = sprintf("%.2f", x))
              },
              par.strip.text = list(cex = .55),
              layout = c(2,4),
              index.cond = list(c(3,4,7,8,5,6,1,2))))
@

### 2012-03-30 mc/plot-interval.Rnw
Typed up changes to paper

\documentclass{article}
\SweaveOpts{prefix.string=plots/interval}
\usepackage[margin=1in]{geometry}

@@

<<>>=
library(fwPackage)
library(lattice)
ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
ltheme$strip.background$col <- "transparent" ## change strip bg  
lattice.options(default.theme = ltheme)      ## set as default

@@

doxyplot <- function(dplot, ...) {
  print(xyplot(I(1 - reject) ~ I(ntest/n) | interaction(nlabel, altlabel, normlabel, sep = ", "),
               data = dplot,
               ylab = "Coverage", xlab = "P/T",
               panel = function(x,y,...) {
                 panel.xyplot(x,y,...,type = "l")
                 panel.lines(c(0,2/3),c(.9,.9), col = "gray")
               },
               layout = c(4,4),
               par.strip.text = list(cex = .65),
               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2))))
}
@

Check empirical coverage of $E_{R} \bar{D}_{1}$ for the one-sided
naive out-of-sample t-test-based interval.
<<testerror1, fig=TRUE, height = 3.5, width=6>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.1', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)

@@

Check empirical coverage of $E_{R} \bar{D}_{1}$ for the two-sided
naive out-of-sample t-test-based interval.
<<testerror2, fig=TRUE, height = 3.5, width=6>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.2', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)
doxyplot(d)
@

Check empirical coverage of $E_{T} \bar{D}_{2}$ for the one-sided
naive out-of-sample t-test-based interval.
<<generror1, fig=TRUE, height = 3.5, width=6>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'gen.error.1', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)
doxyplot(d) #Empirical coverage of one-sided interval
@

Check empirical coverage of $E_{T} \bar{D}_{2}$ for the two-sided
naive out-of-sample t-test-based interval.
<<generror2, fig=TRUE, height = 3.5, width=6>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'gen.error.2', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)
doxyplot(d) #Empirical coverage of two-sided interval
@

>>>>

\documentclass{article}
\SweaveOpts{prefix.string=plots/interval}
\usepackage[margin=1in]{geometry}
\usepackage{tikz}

@@

<<>>=
library(fwPackage)
library(lattice)
library(pgfSweave)
ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
ltheme$strip.background$col <- "transparent" ## change strip bg  
lattice.options(default.theme = ltheme)      ## set as default

@@

doxyplot <- function(dplot,...) {
  print(xyplot(I(1 - reject) ~ I(ntest/n) | interaction(nlabel, altlabel, normlabel, sep = ", "),
               data = dplot,
               ylab = "Coverage", xlab = "$P/T$",
               panel = function(x,y,...) {
                 panel.lines(c(0,2/3),c(.9,.9), col = "gray")
                 panel.xyplot(x,y,...,type = "l")
               },
               layout = c(4,4),
               par.strip.text = list(cex = .55),
               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2))))
}
@

Check empirical coverage of $E_{R} \bar{D}_{1}$ for the one-sided
naive out-of-sample t-test-based interval.
<<testerror1, fig=TRUE, width=6, eps=F, pdf=T>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.1', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)

@@

% Check empirical coverage of $E_{R} \bar{D}_{1}$ for the two-sided
% naive out-of-sample t-test-based interval.
% <<testerror2, fig=TRUE, width=6, tikz=T, eps=F, pdf=T>>=
% d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.2', 500))
% d$nlabel <- sprintf("T=%d", d$n)
% d$normlabel <- sprintf("c=%d", d$norm)
% doxyplot(d)
% @

Check empirical coverage of $E_{T} \bar{D}_{2}$ for the one-sided
naive out-of-sample t-test-based interval.
<<generror1, fig=TRUE, width=6, eps=F, pdf=T>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'gen.error.1', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)
doxyplot(d)
@

% Check empirical coverage of $E_{T} \bar{D}_{2}$ for the two-sided
% naive out-of-sample t-test-based interval.  <<generror2, fig=TRUE,
% width=6, tikz=T, eps=F, pdf=T>>= d <- dbGetQuery(dbc,
% sprintf(dstring, 'gen.error.2', 500)) d$nlabel <-
% sprintf("T=%d", d$n)
% d$normlabel <- sprintf("c=%d", d$norm)
% doxyplot(d) #Empirical coverage of two-sided interval @

### 2012-03-30 mc/plot-oos-size.Rnw
Typed up changes to paper

\documentclass{article}
\SweaveOpts{prefix.string=plots/size}
\usepackage[margin=1in]{geometry}

\begin{document}
Basic file that generates plots for the out-of-sample $t$-test
centered at $E_{R}\bar D_{1}$

<<>>=
library(fwPackage)
library(lattice)
ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
ltheme$strip.background$col <- "transparent" ## change strip bg  
lattice.options(default.theme = ltheme)      ## set as default

@@

doxyplot <- function(dframe, ...) {
  print(xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
               data = dframe,
               ylab = "Rejection Probability", xlab = "P/T",
               panel = function(x,y,...) {
                 panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
                 panel.xyplot(x,y,...,type = "l")
               },
               layout = c(4,4),
               par.strip.text = list(cex = .65),
               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2))))
}
@

Empirical size of Clark and West test at 90\% confidence
<<clarkwest, fig=TRUE, width=6>>=
doxyplot(d[d$transform == "clarkwest",])
@

Empirical size of McCracken test at 90\% confidence
<<mccracken, fig=TRUE, width=6, height=3.5>>=
  print(xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
               data = d[d$altlabel=="K=3" & d$transform == "mccracken",],
               ylab = "Rejection Probability", xlab = "P/T",
               panel = function(x,y,...) {
                 panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
                 panel.xyplot(x,y,...,type = "l")
               },
               layout = c(4,2),
               par.strip.text = list(cex = .65),
               index.cond = list(c(5,7,8,6,1,3,4,2))))
## doxyplot(d[d$altlabel=="K=3" & d$transform == "mccracken",])         
@

Empirical size of Naive OOS test at 90\% confidence
<<dmwsize, fig=TRUE, width=6>>=
doxyplot(d[d$transform == "difference",])
@

Empirical power of Naive oos test at 90\% confidence
<<dmwpower, fig=TRUE, width=6>>=
doxyplot(dpower[dpower$transform == "difference",]) 
@

>>>>

\documentclass{article}
\SweaveOpts{prefix.string=plots/size}
\usepackage[margin=1in]{geometry}
\usepackage{tikz}
\input{../macros}
\begin{document}
Basic file that generates plots for the out-of-sample $t$-test
centered at $E_{R}\bar D_{1}$

<<>>=
library(fwPackage)
library(lattice)
library(pgfSweave)
options(tikzLatexPackages = c(getOption("tikzLatexPackages"),
          "\\input{../macros.tex}"))

ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
ltheme$strip.background$col <- "transparent" ## change strip bg  
lattice.options(default.theme = ltheme)      ## set as default

@@

doxyplot <- function(dframe, ...) {
  print(xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
               data = dframe,
               ylab = "Rejection Probability", xlab = "$P/T$",
               panel = function(x,y,...) {
                 panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
                 panel.xyplot(x,y,...,type = "l")
               },
               layout = c(4,4),
               par.strip.text = list(cex = .55),
               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2))))
}
@

Empirical size of Clark and West test at 90\% confidence
<<clarkwest, fig=TRUE, width=6, tikz=T, eps=F, pdf=T, tikz=T>>=
doxyplot(d[d$transform == "clarkwest",])
@

Empirical size of McCracken test at 90\% confidence
<<mccracken, fig=TRUE, width=6, height=3.5, eps=F, pdf=T, tikz=T>>=
  print(xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
               data = d[d$altlabel=="K=3" & d$transform == "mccracken",],
               ylab = "Rejection Probability", xlab = "$P/T$",
               panel = function(x,y,...) {
                 panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
                 panel.xyplot(x,y,...,type = "l")
               }, layout = c(4,2),
               par.strip.text = list(cex = .55),
               index.cond = list(c(5,7,8,6,1,3,4,2))))
## doxyplot(d[d$altlabel=="K=3" & d$transform == "mccracken",])         
@

Empirical size of Naive OOS test at 90\% confidence
<<dmwsize, fig=TRUE, width=6, eps=F, pdf=T, tikz=T>>=
doxyplot(d[d$transform == "difference",])
@

Empirical power of Naive oos test at 90\% confidence
<<dmwpower, fig=TRUE, width=6, eps=F, pdf=T, tikz=T>>=
doxyplot(dpower[dpower$transform == "difference",])
@
